
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% DENNISE TOHPATI's Resume formatted in LaTex
% Latest Update: 18 March 2023
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basics Document Configurations
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[11pt]{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Header
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\name{Dennise Zefanya Tohpati} % Your name
\address{+44 782-6935-898 | Belfast, United Kingdom} 
\address{
    E-mail: \href{mailto:tohpati.uk@gmail.com}{tohpati.uk@gmail.com} |
    LinkedIn: \href{https://www.linkedin.com/in/tohpati/}{https://www.linkedin.com/in/tohpati/}
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Objectives 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\begin{center}
    Motivated R\&D Engineer with a passion for science \& technologies, and a desire to 
    contribute acquired skills to an engineering role, while gaining industrial and academic experience. 
    Goal-oriented and technically proficient in problem solving, seeking to apply expertise in 
    research and development to a position with a leading engineering firm.
\end{center}
\vspace{2mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Work Experience 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\large \bf Work Experience} \sectionlineskip \hrule
\textbf{Research and Development Engineer} \hfill \textit{(Sept 2021 - Present)}\\
Blow Moulding Technologies, Belfast \hfill \textit{Belfast, UK}\\ 

\vspace{-3mm}
\hspace*{5mm}{\textbf{Digital Twin}}\\
\hspace*{5mm}{
        Part of internal team with role of software and control development lead,
        aim to design Digital Twin technologies of Stretch Blow Moulding Process, long
        term project collaborating with 2 major F\&B manufacturing brand.
    }

\begin{itemize}
    % BScan Automated Contoller --------------------------------------------------------------------------------
    \vspace{-1mm}
    \item {BLOWscan automated controller}
        \vspace{-1.5mm}
        \begin{itemize}
            \item{
                save time up to 90\% to do multiple tests from data preprocess up to postprocessing.
                almost eliminating human interactions.
                }
            \vspace{-2mm}
            \item{
                Also integrating the python into labview environment to work seamlesly.
                }
        \end{itemize}

    
    % Oven Surrogate Model --------------------------------------------------------------------------------
    \vspace{-1mm}
    \item {Oven Surrogate Model:}
        \vspace{-1.5mm}
        \begin{itemize}
            \item{
                Applying and designing architecture for workflow etc
                testing, validating, prepare data, and presented in proper manner. 
                Create optimiser
                }
            \vspace{-2mm}
            \item{
                for reverse engineer machine to make automated decision less than 5 iterations 
                with 99.5\% accuracy to experimental tests
                }
        \end{itemize}
    \vspace{-1mm}
    
    % DT Thickness Gauge
    % Descriptions--------------------------------------------------------------------------------
    \vspace{-1mm}
    \item{TSolver V3} 
        \vspace{-1.5mm}
        \begin{itemize}
            \item{
                Developed a software tool that calculates through-thickness preform 
                temperature profile by translating theoretical knowledge into practical application.
                }
            \vspace{-2mm}
            \item{
                Successfully improved computational efficiency by 500\% compared to previous versions with 
                error less than 2\% to experimental tests.
                }
        \end{itemize}
    \vspace{-1mm}

    % DT TSOLVER Descriptions--------------------------------------------------------------------------------
    \item {Thickness Gauge Controller}
        \vspace{-1.5mm}
        \begin{itemize}
            \item{
                item 1
                }
            \vspace{-3mm}
            \item{
                item 2
                }
        \end{itemize}
    \vspace{-1mm}

\end{itemize}

\vspace{3mm}
\hspace{5mm}\textbf{Digital Catapult: Manufacturing Experiment}\\
\begin{itemize}
    \vspace{-6mm}
    \item {Gain 5000 pounds worth of resources and working together with experimental
    on Artificial intelligence to develop oven surrogate model}
\end{itemize}

% \hspace*{10} - Creep Rig Study \\

\vspace{3mm}
\textbf{MATLAB Student Ambassador} \hfill \textit{(Sept 2020 - June 2021)}\\
MathWorks, Queen's University Belfast\hfill \textit{Belfast, UK (Remote)}\\ 
\begin{itemize}
    \vspace{-5mm}
    \item Established the first MATLAB community on campus to promote and introduce the coding state of art MATLAB as well MathWorks presence at university events.
    \item Demonstrated proficiency in MATLAB and Simulink by planning, hosting, and organising 2-3 training and events per semester on campus
\end{itemize}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% University Based Projects 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{3mm}
{\large \bf University-Based Projects} \sectionlineskip \hrule

\textbf{Queen's Formula Student Aerodynamicist} \hfill \textit{(Sept 2020 - Setp 2021)}\\
Research Team:\\
\begin{itemize}
    \vspace{-5mm}
    \item{
        Designed, analysed, and manufactured the aerodynamic undertray for Queen’s FS 2021. 
        Improved the overall race car’s downforce by 678\% and reduce the drag by 13\%. 
        Interpreted aerodynamics trends and flow features then resulted 
        into a written report as part of final project.
        }
    \item{
        Demonstrated proficiency of component design analysis process; 
        surfacing, meshing, validation, and verification using Solidworks and 
        ANSYS Workbench to achieve the high-performance undertray design.
        }
    \item{
        Developed strong foundation in Computational Fluid Dynamics by prepared and 
        analysed undertray geometries \& mesh on both 2D-3D, and utilised post-processing 
        CFD to generate presentable graph trend and flow graphics.
        }
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\large \bf Educational Background} \sectionlineskip \hrule % horizontal line

\textbf{Bachelor of Engineering: Aerospace Engineering} \hfill \textit{(Sept 2018 - June 2021)}\\
Queen's University Belfast, Belfast \hfill \textit{Belfast, UK}\\ 
\vspace{-6mm}
\begin{itemize}
    \item{Top the class 2021 \& Top thesis 2021 | Overall Score: 80}\%
\end{itemize}


\textbf{Foundation in Engineering and Science} \hfill \textit{(Sept 2017 - June 2018)}\\
INTO Queen's University Belfast, Belfast \hfill \textit{Belfast, UK} \\ 
\vspace{-6mm}
\begin{itemize}
    \item{Overall Score: 84.25\%}
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Achievements 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\large \bf Achievements} \sectionlineskip \hrule 
\begin{itemize}
    \item{
        Annual Highest-Average Mark Awards: Royal Aeronautical Society Prize (Final Year/Stage 3), 
        Foundation Scholarship (Stage 2), Bombardier Stage One Award (Stage 1), 
        INTO Excellence Student Award (University Foundation).
        }
    \vspace{-1mm}
    \item{
        200 hours Millennial volunteer Award: given as a young person starts 
        at 51 hours and gains recognition as reached 200 hours of volunteering commitment.
    }
    \vspace{-1mm}
    \item{
        Inspiring Leaders: given as an active organisational member 
        who held a position and requires a leadership role.}
\end{itemize}

\begin{center}
    \vspace{2mm}
    \small{\bf References are available upon requests}
\end{center}




\end{document}
